\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-16 doc/paper.tex
mini edits
i am not sure what changes i am commiting

Bullet matching methods are usually based on these associated
signatures. \citet{chu2013} use an automatic method for counting
consecutive matching striae (CMS). The authors report an error rate of
52\% of the known same source lands comparisons as misidentified (false
negative) and zero false positives for known different source lands.
\citet{ma2004} and \citet{vorburger2011} discuss CCF (cross-correlation
function) and its discriminating power and applicability for same-source
analyses of bullets, but do not provide any error rates in their
discussion. \citet{aoas} use multiple features like CCF, CMS, D
(distance measure) etc in a random forest based method and compare every
land against every other land of digitised versions of Hamby 252 and
Hamby 44 \citep{hamby} published on the NIST Ballistics Database
\citep{nist}. The authors report an out-of-bag overall error rate of
0.46\%, comprised of a false positive error rate of 30.05\% and a false
negative rate of 0.026\%.

The Chumbley score provides us with another approach in the same-source
assessment of bullet striation marks. \citet{chumbley} compare two
toolmarks for same-source. The data for this study was obtained from 50
sequentially manufactured screwdriver tips. \citet{chumbley} report
error rates for markings made by the tips at different angles. For
markings made under a 30 degree the authors report an average false
negative error rate of 0.023 and an average false positive error rate of
0.09. For other angles the error rates for false negatives stay the same
while the rate of false positives decreases to 0.01.
\hh{are the angles steeper?} The paper by \citet{hadler} is based on the
same data but the authors focus on markings made under the same angle.
The error rates associated with the deterministic version of the score
are 0.06 for false negatives and a false poisitive error rate of 0.

@@

Comparisons of striae from bullets are usually based on comparisons of
striae in land engraved areas, which are extracted in form of cross
sections, called \emph{profiles} \citep{aoas,ma2004}. From profiles
bullet \emph{signatures} \citep{chu2013,aoas} are extracted as residuals
of a loess fit or Gaussian filter. Signatures are considered to be noise
free and a good reflection of the key attributes of the raw marking, and
the unique features of a bullet.
\hh{Do you have a reference for the previous sentenced?} A detailed
discussion of the extraction technique for signatures is given in
\citet{aoas}.

@@

\subsection{Potential Challenges in Chumbley Score
Adaptation}\label{potential-challenges-in-chumbley-score-adaptation}

\hh{The Chumbley score allows a separation of a toolmark into raw and normalized digitized versions. Originally, this mechanism is intended to separate between class characteristics and individual markings, however, in the setting of matching bullet striae, we could also use it to separate bullet curvature in profiles from signatures before matching signatures. }

@@

In a pre-processing step the two markings are smoothed using a lowess
\citep{lowess} with coarseness parameter \(c\). The purpose of this
smoothing is to remove drift and (sub)class characteristics.

The Chumbley scores is calculated in two phases, namely, an optimization
step and a validation step. In the optimization step, the two markings
are aligned horizontally such that within a pre-defined window of length
\(w_o\) the correlation between \(x(t_1)\) and \(y(t_2)\) is maximized:
\[
\left(t_1^o, t_2^o\right) = \mathop{\arg \max}\limits_{1 \le t_1 \le T_1, 1 \le t_2 \le T_2} \text{cor} \left(x (t_1, t_1 + w_o), y(t_2, t_2 + w_o) \right)
\] This results in an optimal vertical (in-phase) shift of
\(t_1^o - t_2^o\) for aligning the two markings.

@@

\begin{center}\includegraphics[width=\textwidth]{figures/profile-sketch-1} \end{center}

>>>>

Bullet matching methods are usually based on these associated
signatures. \citet{chu2013} use an automatic method for counting
consecutive matching striae (CMS). The authors report an error rate of
52\% of the known same source lands comparisons as misidentified (false
negative) and zero false positives for known different source lands.
\citet{ma2004} and \citet{vorburger2011} discuss CCF (cross-correlation
function) and its discriminating power and applicability for same-source
analyses of bullets, but do not provide any error rates in their
discussion. \citet{aoas} use multiple features like CCF, CMS, D
(distance measure) etc in a random forest based method and compare every
land against every other land of digitised versions of Hamby 252 and
Hamby 44 \citep{hamby} published on the NIST Ballistics Database
\citep{nist}. The authors report an out-of-bag overall error rate of
0.46\%, comprised of an error rate of 30.05\% of same-source pairs that
were not identified and an error rate of 0.026\% of different-source
pairs that were incorrectly identified as same-source.

The Chumbley score provides us with another approach in the same-source
assessment of bullet striation marks. \citet{chumbley} compare two
toolmarks for same-source. The data for this study was obtained from 50
sequentially manufactured screwdriver tips. \citet{chumbley} report
error rates for markings made by the tips at different angles. For
markings made at 30 degree the authors report an average false negative
error rate of 0.089 and an average false positive error rate of 0.023.
For other angles of 60 and 85 degrees the false negatives error rate is
0.09 while the rate of false positives decreases to 0.01. The paper by
\citet{hadler} is based on the same data but the authors focus on
markings made under the same angle. The error rates associated with the
deterministic version of the score are 0.06 for false negatives and a
false positive error rate of 0.

@@

Comparisons of striae from bullets are usually based on comparisons of
striae in land engraved areas, which are extracted in form of cross
sections, called \emph{profiles} \citep{aoas,ma2004}. From profiles
bullet \emph{signatures} \citep{chu2013,aoas} are extracted as residuals
of a loess fit or Gaussian filter. This effectively removes topographic
structure from the data in the attempt to increase the signal to noise
ratio. The span of the loess fit was found using cross-validation, as
described by \citet{aoas}.

@@

@@

In a pre-processing step the two markings are smoothed using a lowess
\citep{lowess} with coarseness parameter \(c\). Originally, this
smoothing is intended to remove drift and (sub)class characteristics
from individual markings, however, in the setting of matching bullet
striae, we can also make use of this mechanism can be used to separate
bullet curvature in profiles from signatures before matching signatures.

After removing sub-class structure, the Chumbley scores is calculated in
two steps: an optimization step and a validation step. In the
optimization step, the two markings are aligned horizontally such that
within a pre-defined window of length \(w_o\) the correlation between
\(x(t_1)\) and \(y(t_2)\) is maximized: \[
\left(t_1^o, t_2^o\right) = \mathop{\arg \max}\limits_{1 \le t_1 \le T_1, 1 \le t_2 \le T_2} \text{cor} \left(x (t_1, t_1 + w_o), y(t_2, t_2 + w_o) \right)
\] This results in an optimal vertical (in-phase) shift of
\(t_1^o - t_2^o\) for aligning the two markings.

@@

{\centering \includegraphics[width=\textwidth]{figures/profile-sketch-1}

\caption{Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \ref{fig:sigs-profiles}. }\label{fig:profile-sketch}
\end{figure}
